Master's Project Journal

### 2019-04-24 thesis/NetworkImplemenation.tex
citation and tables
done done

The error combiner was designed to take in up to four error signals, all of an identical width which defaults to eight, and four weights to apply in the summation process. A weighted summation is performed by multiplying each error signal by the weight and adding the results together. Regardless of the number of input error signals, a division by four is then performed in order to compute the average error, done by shifting the value right by two. In \iac{HDL}, unlike C programming or similar, a shift requires no computation and is instead implemented by performing a part-selection. As all error signals are two's complemented signed integers, the error combination process is also carried out using signed values. The code implementing the error combiner can be found in \textsc{ErrorCombiner.v}, attached in Appendix \ref{adx:code} Listing \ref{lst:error_combiner}.

@@

Figure \ref{fig:integer_lf} contains \iac{RTL} diagram describing the implementation. Important to note, is the shift applied to the result of the multiplication by \acs{kp} which, as the integration is performed with a larger width to avoid accumulator overflow, preserves the intended relationship between proportional and integral gains. The value of $k_p$ and $k_i$ can be computed using the following formulae:
\begin{gather}
\text{Proportional gain} = k_p\times 2^{-path\_width\_change\_p} \\
path\_width\_change\_p = lsh\_width - rsh\_width \\
lsh\_width = ki\_width - kp\_width  \\
rsh\_width = error\_width + kp\_width + lsh\_width - control\_code\_width \\
\text{Integral gain} = k_i\times 2^{-path\_width\_change\_i} \\
path\_width\_change\_i = - rsh\_width
\end{gather}
In the example system shown in Figure \ref{fig:integer_lf} the proportional gain can be computed as $k_p\times 2^{3-8} = \frac{k_p}{32}$ and the integral gain is $k_i\times 2^{-8} = \frac{k_i}{128}$.
The Verilog implementation of the \ac{LF} using integer arithmetic can be found in \textsc{LoopFilter.v}, attached in Appendix \ref{adx:code} Listing \ref{lst:loop_filter}.

@@

\subsubsection{Phase Detector}
As previously mentioned the \ac{PFD} is also implemented using the \ac{FPGA} clocked approach, with sign detection carried out using a Moore Machine. The state transition diagram given as the example in Chapter \ref{chap:3} is that used to design this sign detector. The hardware description of this block is found in \textsc{PhaseDetector.v}, attached in Appendix \ref{adx:code} Listing \ref{lst:PhaseDetector}.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{../state_trans_new}
    \caption[Example State Transition Diagram for a Moore Machine]{Example State Transition Diagram for a Moore Machine.}
    \label{fig:state_trans_reprint}
\end{figure}

@@

\subsubsection{\acs{ADPLL} 1 Design Summary}
The listed components were brought together in \textsc{NetworkADPLL.v}, attached in Appendix \ref{adx:code} Listing \ref{lst:network_adpll}. It is important to note that each \ac{ADPLL} contains only two \aclp{PD}, despite the fact that during network operation the need for phase comparisons to be made with up to four neighbours. The two ``missing'' \acp{PD} are in fact synthesised as part of the other \acp{ADPLL}, with which the comparison would be made. This allows for a 50\% reduction in the number of \acp{PD} required, while also ensuring identical error is received by both \acp{ADPLL}. Each \ac{ADPLL} performs comparison with the \ac{DCO} ``above'' and ``left'' of them in the Cartesian grid, and a port in the module outputs the results for use by the other \acp{ADPLL} involved.
Table \ref{table:adpll1} contains a brief overview of the bit widths, tuning ranges and other configuration information for this \ac{ADPLL}.
\begin{table}[!h]
    \begin{center}
        \begin{tabular}{|l|r|r|r|}
            \multicolumn{4}{c}{\ac{DCO} Tuning Range} \T\\
            \hline
            \multicolumn{1}{|c|}{-} & \multicolumn{1}{c|}{Minimum} & \multicolumn{1}{c|}{Step} & \multicolumn{1}{c|}{Maximum} \T\\
            \hline
            Frequency & $1.008~\si{\mega\hertz}$ & \multicolumn{1}{r|}{$62.988~\si{\kilo\hertz}$} & $8.944~\si{\mega\hertz}$ \T\\
            \hline
            Period & $992.0~\si{\nano\second}$ & \multicolumn{1}{r|}{$2.5~\si{\nano\second}$ (at $5~\si{\mega\hertz}$)} & $111.8~\si{\nano\second}$ \T\\
            \hline
        \end{tabular}
        \begin{tabular}{|l|r|l|r|}
            \multicolumn{4}{c}{Configuration as Implemented} \T\\
            \hline
            \ac{DCO} Counter Width & 12 bits & \ac{DCO} Control Width (max) & 12 bits \T\\
            \hline
            \ac{DCO} Bias Point & 79 & Runtime Gains & Enabled \T\\
            \hline
            Phase Detector Error Width & 7 & Error Sum Weight Width & 4 \T\\
            \hline
            \acs{kp} width & 5 & \acs{ki} & 8 \T\\
            \hline
            \acs{kp} & $2^{-5}\times[0,15]\cap\mathbb{Z}$ & \acs{ki} & $2^{-8}\times[0,15]\cap\mathbb{Z}$ \T\\
            \hline
            Detection Resolution & $3.875~\si{\nano\second}$ & Detection Phase Resolution & $6.975\si{\degree}$ (at $5~\si{\mega\hertz}$)\\
            \hline
        \end{tabular}
    \end{center}
\caption[ADPLL Design 1 Summary]{ADPLL Design 1 Summary.}
\label{table:adpll1}
\end{table}

\subsection{\acs{ADPLL} Design 2}
The second \ac{ADPLL} design implemented during the course of this project was sa stepping stone between fully synchronous and asynchronous to the \ac{FPGA} clock. The clocked phase detector is reused from above, albeit with an altered error width, while the \ac{DCO} is replaced by \iacl{RO}. While the phase detector was known to work due to testing in \ac{ADPLL} 1, the \ac{DCO} could not be simulated using accurate timings, so all testing had to be done in hardware. This presented a challenge, as depending on the implementation, the characteristics of the \ac{DCO} could change, most importantly the centre frequency. The module implementing this \ac{ADPLL} can be found in \textsc{NetworkRingADPLL.v}, attached in Appendix \ref{adx:code} Listing \ref{lst:network_ring_adpll}.

@@

The module implementing the \ac{RO} can be found in \textsc{RingOsc.v}, attached in Appendix \ref{adx:code} Listing \ref{lst:ring_osc}. In the module instance statement, it can be seen that a second generated output is also present. This second output is taken from a point in the fixed part of the chain, a significant number of inverters prior to the minimum number of inverters removable by the control code adjustment. This signal is at an identical frequency to that of the generated signal, however will not be immediately affected by a change in the control code, which could in some edge cases change the polarity of the signal. This signal is used to drive the \ac{LF} in order to avoid an extraneous addition to the accumulator in the integral path. This early signal must be taken from an inverter at an index significantly lower than $n-k$ to prevent this addition causing the problem it has been implemented to avoid.

@@

\begin{table}[!h]
    \begin{center}
        \begin{tabular}{|l|r|r|r|}
            \multicolumn{4}{c}{\ac{DCO} Tuning Range} \T\\
            \hline
            \multicolumn{1}{|c|}{-} & \multicolumn{1}{c|}{Minimum} & \multicolumn{1}{c|}{Step} & \multicolumn{1}{c|}{Maximum} \T\\
            \hline
            Frequency & $4.571~\si{\mega\hertz}$ & $29.180~\si{\kilo\hertz}$ (at $5~\si{\mega\hertz}$) & $5.518~\si{\mega\hertz}$ \T\\
            \hline
            Period & $218.2~\si{\nano\second}$ & $1.176~\si{\nano\second}$ & $181.1~\si{\nano\second}$ \T\\
            \hline
        \end{tabular}
        \begin{tabular}{|l|r|l|r|}
            \multicolumn{4}{c}{Configuration as Implemented} \T\\
            \hline
            \ac{RO} num. of inverters (max) & 373 & \ac{RO} Control Width & 5 bits \T\\
            \hline
            \ac{RO} Bias Point & 16 & Runtime Gains & Enabled \T\\
            \hline
            Phase Detector Error Width & 5 & Error Sum Weight Width & 4 \T\\
            \hline
            \acs{kp} width & $4$ & \acs{ki} & $6$ \T\\
            \hline
            \acs{kp} & $2^{-4}\times[0,15]\cap\mathbb{Z}$ & \acs{ki} & $2^{-6}\times[0,15]\cap\mathbb{Z}$ \T\\
            \hline
            Detection Resolution & $3.875~\si{\nano\second}$ & Detection Phase Resolution & $6.975\si{\degree}$ (at $5~\si{\mega\hertz}$)\\
            \hline
        \end{tabular}
    \end{center}
    \caption[\ac{ADPLL} Design 2 Summary]{\ac{ADPLL} Design 2 Summary.}
    \label{table:adpll2}
\end{table}

\subsection{\acs{ADPLL} Design 3}
\acs{ADPLL} Design 3 has no dependence on the clock provided by the \ac{FPGA}'s clock management utility, as both the \ac{RO} and the \ac{TDC} are designed using inverters, while a Bang-Bang detector replaces the \ac{FPGA} clock reliant \ac{FSM} of the two previous designs. This introduces a second source of implementation based variation between \acp{ADPLL}, however, this has significantly less impact on the frequency range of the oscillator and no impact at all on the centre frequencies. The lack of \iac{FPGA} clocked element means this design will have the closest behaviour to that of \iac{ASIC} based \ac{ADPLL} implementation, although as the level of variation due to implementation is much larger on \iac{FPGA}, the impact of non-idealities will be exaggerated.
%same interface
In order to allow quick exchange of \acp{PD} or other modules, the module in which this \ac{ADPLL} is implemented still retains the \ac{FPGA} clock as an input. In fact, this module shares its implementation with that of \ac{ADPLL} 2, as while the \ac{PD} designs are drastically different, the interface is identical. This allows for the changing of \ac{PD} purely by changing the module type in the instance statement. The module implementing this \ac{ADPLL} can be found in \textsc{NetworkRingADPLL.v}, attached in Appendix \ref{adx:code} Listing \ref{lst:network_ring_adpll}.

@@

%TODO eugene
The delay line itself is shown in Figure \ref{fig:tdl_impl}, with each tap implemented by a pair of flip-flops and three inverters. For an $N$ bit width phase error detection, $2^{N-1}-1$ taps are required. In the case of this \ac{ADPLL}, a 5 bit two's complement error signal is required, thus the range of the signal is $[-16,15]\cap\mathbb{Z}$. If the range is made symmetrical, 15 taps are required to fill a signal of this size. From the diagram, it can be seen that unless edges are detected on each signal at exactly the same instant, it is almost impossible to measure a zero phase difference between reference and generated signals. This is an intentional decision, \cite{idkwhattocite}.
\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{../new_pdet2}
    \caption[Inverter based \ac{TDL} RTL diagrams]{Inverter based \ac{TDL} RTL diagrams.}
    \label{fig:tdl_impl}
\end{figure}
The operation of the \ac{TDL} is as follows: A delayed version of the \texttt{count} signal acts as the clock for flip-flops forming each tap, which are rising edge activated. These flip-flops have a constant ``1'' at their $D$ inputs, so as the signal propagates through the delay line, each flip-flop will assign a logic ``1'' to their corresponding \texttt{error\_tap[i]} signal. When the measurement interval has completed, the \texttt{count} signal clocks the 15 bit wide \texttt{error\_tap} signal into \texttt{error\_tap\_buff}. These flip-flops act as the output buffers of the \ac{PD}, holding the phase error constant between measurement intervals. As with the flip-flops performing edge detection, the flip-flops comprising the taps can only be used once before requiring a reset, which is again carried out using the \texttt{done} signal. As flip-flops have a hold time, the duration after the clock edge in which the signal applied at the $D$ input must not change to ensure valid data, an inverter is used to delay the reset to avoid a violation.

@@

The now unsigned binary representation of the error magnitude can be combined then with the sign bit to form a two's complement error signal. The file \textsc{PhaseDetectorDL.v} in Appendix \ref{adx:code} Listing \ref{lst:phase_detector_dl} contains the Verilog implementation of this module. \texttt{DONT\_TOUCH} compiler directives were used here in a number of places to ensure that the inverters and other elements that are key for timing are not removed in the synthesis process, as similarly to \ac{RO}, Vivado sees these as unneeded elements serving no purpose.

>>>>

The error combiner was designed to take in up to four error signals, all of an identical width which defaults to eight, and four weights to apply in the summation process. A weighted summation is performed by multiplying each error signal by the weight and adding the results together. Regardless of the number of input error signals, a division by four is then performed in order to compute the average error, done by shifting the value right by two. In \iac{HDL}, unlike C programming or similar, a shift requires no computation and is instead implemented by performing a part-selection. As all error signals are two's complemented signed integers, the error combination process is also carried out using signed values. The code implementing the error combiner can be found in \textsc{ErrorCombiner.v}, attached in Appendix  \ref{lst:error_combiner}.

@@

Figure \ref{fig:integer_lf} contains \iac{RTL} diagram describing the implementation. Important to note, is the shift applied to the result of the multiplication by \acs{kp} which, as the integration is performed with a larger width to avoid accumulator overflow, preserves the intended relationship between proportional and integral gains. The value of $k_p$ and $k_i$ can be computed using the following formulae:
\begin{gather}
\text{Proportional gain} = k_p\times 2^{-path\_width\_change\_p} \\
path\_width\_change\_p = lsh\_width - rsh\_width \\
lsh\_width = ki\_width - kp\_width  \\
rsh\_width = error\_width + kp\_width + lsh\_width - control\_code\_width \\
\text{Integral gain} = k_i\times 2^{-path\_width\_change\_i} \\
path\_width\_change\_i = - rsh\_width
\end{gather}
In the example system shown in Figure \ref{fig:integer_lf} the proportional gain can be computed as $k_p\times 2^{3-8} = \frac{k_p}{32}$ and the integral gain is $k_i\times 2^{-8} = \frac{k_i}{128}$.
The Verilog implementation of the \ac{LF} using integer arithmetic can be found in \textsc{LoopFilter.v}, attached in Appendix \ref{lst:loop_filter}.

@@

\subsubsection{Phase Detector}
As previously mentioned the \ac{PFD} is also implemented using the \ac{FPGA} clocked approach, with sign detection carried out using a Moore Machine. The state transition diagram given as the example in Chapter \ref{chap:3} is that used to design this sign detector. The hardware description of this block is found in \textsc{PhaseDetector.v}, attached in Appendix \ref{lst:PhaseDetector}.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{../state_trans_new}
    \caption[Example State Transition Diagram for a Moore Machine]{Example State Transition Diagram for a Moore Machine.}
    \label{fig:state_trans_reprint}
\end{figure}

@@

\subsubsection{\acs{ADPLL} 1 Design Summary}
The listed components were brought together in \textsc{NetworkADPLL.v}, attached in Appendix \ref{lst:network_adpll}. It is important to note that each \ac{ADPLL} contains only two \aclp{PD}, despite the fact that during network operation the need for phase comparisons to be made with up to four neighbours. The two ``missing'' \acp{PD} are in fact synthesised as part of the other \acp{ADPLL}, with which the comparison would be made. This allows for a 50\% reduction in the number of \acp{PD} required, while also ensuring identical error is received by both \acp{ADPLL}. Each \ac{ADPLL} performs comparison with the \ac{DCO} ``above'' and ``left'' of them in the Cartesian grid, and a port in the module outputs the results for use by the other \acp{ADPLL} involved.
Table \ref{table:adpll1} contains a brief overview of the bit widths, tuning ranges and other configuration information for this \ac{ADPLL}.
\begin{table}[!h]
    \begin{center}
        \begin{tabular}{|l|r|r|r|}
            \multicolumn{4}{c}{\ac{DCO} Tuning Range} \T\\
            \hline
            \multicolumn{1}{|c|}{-} & \multicolumn{1}{c|}{Minimum} & \multicolumn{1}{c|}{Step} & \multicolumn{1}{c|}{Maximum} \T\\
            \hline
            Frequency & $1.008~\si{\mega\hertz}$ & \multicolumn{1}{r|}{$62.988~\si{\kilo\hertz}$} & $8.944~\si{\mega\hertz}$ \T\\
            \hline
            Period & $992.0~\si{\nano\second}$ & \multicolumn{1}{r|}{$2.5~\si{\nano\second}$ (at $5~\si{\mega\hertz}$)} & $111.8~\si{\nano\second}$ \T\\
            \hline
        \end{tabular}
        \begin{tabular}{|l|r|l|r|}
            \multicolumn{4}{c}{Configuration as Implemented} \T\\
            \hline
            \ac{DCO} Counter Width & 12 bits & \ac{DCO} Control Width (max) & 12 bits \T\\
            \hline
            \ac{DCO} Bias Point & 79 & Runtime Gains & Enabled \T\\
            \hline
            Phase Detector Error Width & 7 & Error Sum Weight Width & 4 \T\\
            \hline
            \acs{kp} width & 5 & \acs{ki} & 8 \T\\
            \hline
            \acs{kp} & $2^{-5}\times[0,15]\cap\mathbb{Z}$ & \acs{ki} & $2^{-8}\times[0,15]\cap\mathbb{Z}$ \T\\
            \hline
            Detection Resolution & $3.875~\si{\nano\second}$ & Detection Phase Resolution & $6.975\si{\degree}$ (at $5~\si{\mega\hertz}$)\\
            \hline
        \end{tabular}
    \end{center}
\caption[ADPLL Design 1 Summary]{ADPLL Design 1 Summary.}
\label{table:adpll1}
\end{table}

\subsection{\acs{ADPLL} Design 2}
The second \ac{ADPLL} design implemented during the course of this project was sa stepping stone between fully synchronous and asynchronous to the \ac{FPGA} clock. The clocked phase detector is reused from above, albeit with an altered error width, while the \ac{DCO} is replaced by \iacl{RO}. While the phase detector was known to work due to testing in \ac{ADPLL} 1, the \ac{DCO} could not be simulated using accurate timings, so all testing had to be done in hardware. This presented a challenge, as depending on the implementation, the characteristics of the \ac{DCO} could change, most importantly the centre frequency. The module implementing this \ac{ADPLL} can be found in \textsc{NetworkRingADPLL.v}, attached in Appendix \ref{lst:network_ring_adpll}.

@@

The module implementing the \ac{RO} can be found in \textsc{RingOsc.v}, attached in Appendix \ref{lst:ring_osc}. In the module instance statement, it can be seen that a second generated output is also present. This second output is taken from a point in the fixed part of the chain, a significant number of inverters prior to the minimum number of inverters removable by the control code adjustment. This signal is at an identical frequency to that of the generated signal, however will not be immediately affected by a change in the control code, which could in some edge cases change the polarity of the signal. This signal is used to drive the \ac{LF} in order to avoid an extraneous addition to the accumulator in the integral path. This early signal must be taken from an inverter at an index significantly lower than $n-k$ to prevent this addition causing the problem it has been implemented to avoid.

@@

\begin{table}[!h]
    \begin{center}
        \begin{tabular}{|l|r|r|r|}
            \multicolumn{4}{c}{\ac{DCO} Tuning Range} \T\\
            \hline
            \multicolumn{1}{|c|}{-} & \multicolumn{1}{c|}{Minimum} & \multicolumn{1}{c|}{Step} & \multicolumn{1}{c|}{Maximum} \T\\
            \hline
            Frequency & $4.571~\si{\mega\hertz}$ & $29.180~\si{\kilo\hertz}$ (at $5~\si{\mega\hertz}$) & $5.518~\si{\mega\hertz}$ \T\\
            \hline
            Period & $218.2~\si{\nano\second}$ & $1.176~\si{\nano\second}$ & $181.1~\si{\nano\second}$ \T\\
            \hline
        \end{tabular}
        \begin{tabular}{|l|r|l|r|}
            \multicolumn{4}{c}{Configuration as Implemented} \T\\
            \hline
            \ac{RO} num. of inverters (max) & 373 & \ac{RO} Control Width & 5 bits \T\\
            \hline
            \ac{RO} Bias Point & 16 & Runtime Gains & Enabled \T\\
            \hline
            Phase Detector Error Width & 5 & Error Sum Weight Width & 4 \T\\
            \hline
            \acs{kp} width & $4$ & \acs{ki} & $6$ \T\\
            \hline
            \acs{kp} & $2^{-4}\times[0,15]\cap\mathbb{Z}$ & \acs{ki} & $2^{-6}\times[0,15]\cap\mathbb{Z}$ \T\\
            \hline
            Detection Resolution & $3.875~\si{\nano\second}$ & Detection Phase Resolution & $6.975\si{\degree}$ (at $5~\si{\mega\hertz}$)\\
            \hline
        \end{tabular}
    \end{center}
    \caption[\acs{ADPLL} Design 2 Summary]{\acs{ADPLL} Design 2 Summary.}
    \label{table:adpll2}
\end{table}

\subsection{\acs{ADPLL} Design 3}
\acs{ADPLL} Design 3 has no dependence on the clock provided by the \ac{FPGA}'s clock management utility, as both the \ac{RO} and the \ac{TDC} are designed using inverters, while a Bang-Bang detector replaces the \ac{FPGA} clock reliant \ac{FSM} of the two previous designs. This introduces a second source of implementation based variation between \acp{ADPLL}, however, this has significantly less impact on the frequency range of the oscillator and no impact at all on the centre frequencies. The lack of \iac{FPGA} clocked element means this design will have the closest behaviour to that of \iac{ASIC} based \ac{ADPLL} implementation, although as the level of variation due to implementation is much larger on \iac{FPGA}, the impact of non-idealities will be exaggerated.
%same interface
In order to allow quick exchange of \acp{PD} or other modules, the module in which this \ac{ADPLL} is implemented still retains the \ac{FPGA} clock as an input. In fact, this module shares its implementation with that of \ac{ADPLL} 2, as while the \ac{PD} designs are drastically different, the interface is identical. This allows for the changing of \ac{PD} purely by changing the module type in the instance statement. The module implementing this \ac{ADPLL} can be found in \textsc{NetworkRingADPLL.v}, attached in Appendix \ref{lst:network_ring_adpll}.

@@

%TODO eugene
The delay line itself is shown in Figure \ref{fig:tdl_impl}, with each tap implemented by a pair of flip-flops and three inverters. For an $N$ bit width phase error detection, $2^{N-1}-1$ taps are required. In the case of this \ac{ADPLL}, a 5 bit two's complement error signal is required, thus the range of the signal is $[-16,15]\cap\mathbb{Z}$. If the range is made symmetrical, 15 taps are required to fill a signal of this size. From the diagram, it can be seen that unless edges are detected on each signal at exactly the same instant, it is almost impossible to measure a zero phase difference between reference and generated signals. This is done to maximize the information carried by the digital signal \cite{shan2014phd}.
\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{../new_pdet2}
    \caption[Inverter based \ac{TDL} RTL diagrams]{Inverter based \ac{TDL} RTL diagrams.}
    \label{fig:tdl_impl}
\end{figure}
The operation of the \ac{TDL} is as follows: A delayed version of the \texttt{count} signal acts as the clock for flip-flops forming each tap, which are rising edge activated. These flip-flops have a constant ``1'' at their $D$ inputs, so as the signal propagates through the delay line, each flip-flop will assign a logic ``1'' to their corresponding \texttt{error\_tap[i]} signal. When the measurement interval has completed, the \texttt{count} signal clocks the 15 bit wide \texttt{error\_tap} signal into \texttt{error\_tap\_buff}. These flip-flops act as the output buffers of the \ac{PD}, holding the phase error constant between measurement intervals. As with the flip-flops performing edge detection, the flip-flops comprising the taps can only be used once before requiring a reset, which is again carried out using the \texttt{done} signal. As flip-flops have a hold time, the duration after the clock edge in which the signal applied at the $D$ input must not change to ensure valid data, an inverter is used to delay the reset to avoid a violation.

@@

The now unsigned binary representation of the error magnitude can be combined then with the sign bit to form a two's complement error signal. The file \textsc{PhaseDetectorDL.v} in Appendix \ref{lst:phase_detector_dl} contains the Verilog implementation of this module. \texttt{DONT\_TOUCH} compiler directives were used here in a number of places to ensure that the inverters and other elements that are key for timing are not removed in the synthesis process, as similarly to \ac{RO}, Vivado sees these as unneeded elements serving no purpose.

### 2019-04-24 thesis/TestingAnalysis.tex
done done

As Table \ref{table:accum_width} shows, while the resolution may have improved, the jitter has not. This occurs as all signals are synchronised to the \ac{FPGA} clock, which has a $3.875~\si{\nano\second}$ period. This quantises the output waveform to the \ac{FGPA} clock, and sets the minimum bound on the jitter. Accordingly, the most suitable counter width is that which maximises the bit width, and thus achieves the best frequency resolution, with the constraint that, at the operating frequency, the a period resolution is no finer than the \ac{FPGA} clock period. In this case, there is no bit width that satisfies both constraints, so the latter is relaxed to get a width of $12$.
%TODO explanation for this?
\begin{table}[!ht]
    \begin{center}
        \begin{footnotesize}
            \setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{ll|r|r|r|r|r|r|r|r|r|}           
                \cline{3-11}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error (ns)} & \multicolumn{3}{c|}{Skew (ns)} \T\\
                \cline{3-11} 
                &&PLL 11&PLL 12&PLL 22    &PLL 11&PLL 12&PLL 22    &PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Accum. Width 12}&-&-&-&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &1.7693 &1.8463 &1.8862    &7.3060  &7.2565  &10.151    &2.2791 &1.2822  &1.6299  \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.9964 &1.9146 &1.9572    &15.0890 &18.2830 &19.673    &9.2449 &11.6120 &12.0520 \T\\
                \hline
                \multicolumn{2}{|l|}{Accum. Width 13}&-&-&-&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &1.7946 &1.8161 &1.9048    &6.8614  &7.1495 &9.371      &2.2257 &1.6328  &1.3778  \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &2.0016 &1.9217 &1.9605    &14.9580 &18.938 &19.510     &9.1678 &12.0000 &11.7690 \T\\
                \hline
                \B
            \end{tabular}
        \end{footnotesize}
        \caption{\ac{DCO} Accumulator Width Comparison.}
        \label{table:accum_width}
    \end{center}
    \vspace{-0.5cm}
\end{table}
%\FloatBarrier

>>>>

As Table \ref{table:accum_width} shows, while the resolution may have improved, the jitter has not. In this design, all signals are synchronised to the \ac{FPGA} clock, which has a $3.875~\si{\nano\second}$ period. The output waveform can only change at rising edges of the \ac{FPGA} clock, thus quantising the generated signal's period to increments of $3.875~\si{\nano\second}$. If the period step is shorter than the clock period, the extra resolution is lost and the \ac{FPGA} clock sets the minimum bound on the jitter. Accordingly, the most suitable counter width is that which maximises the number of bits, and thus achieves the best frequency resolution, with the constraint that, at the operating frequency, the period resolution is no finer than the \ac{FPGA} clock period. In this case, there is no bit width that satisfies both constraints, so the latter is relaxed to get a width of $12$.

\begin{table}[!ht]
    \begin{center}
        \begin{footnotesize}
            \setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{ll|r|r|r|r|r|r|r|r|r|}           
                \cline{3-11}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error (ns)} & \multicolumn{3}{c|}{Skew (ns)} \T\\
                \cline{3-11} 
                &&PLL 11&PLL 12&PLL 22    &PLL 11&PLL 12&PLL 22    &PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Accum. Width 12}&-&-&-&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &1.7693 &1.8463 &1.8862    &7.3060  &7.2565  &10.151    &2.2791 &1.2822  &1.6299  \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.9964 &1.9146 &1.9572    &15.0890 &18.2830 &19.673    &9.2449 &11.6120 &12.0520 \T\\
                \hline
                \multicolumn{2}{|l|}{Accum. Width 13}&-&-&-&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &1.7946 &1.8161 &1.9048    &6.8614  &7.1495 &9.371      &2.2257 &1.6328  &1.3778  \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &2.0016 &1.9217 &1.9605    &14.9580 &18.938 &19.510     &9.1678 &12.0000 &11.7690 \T\\
                \hline
                \B
            \end{tabular}
        \end{footnotesize}
        \caption{\acs{DCO} Accumulator Width Comparison.}
        \label{table:accum_width}
    \end{center}
    \vspace{-0.5cm}
\end{table}
%\FloatBarrier
